Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-02 WSSSPE3/report/WSSSPE3_review.tex
Section 2: Minor rewriting.

The first call for participation requested lightning talks, where each author
could make a brief statement about work that either had been done or was needed,
with the goal of contributing to the discussion of one or more working groups.
There were~24 lightning talks submitted, and, after a peer-review process, 16 of
those were accepted, as discussed further in Section~\ref{sec:lightning}.

>>>>

The first call for participation requested lightning talks, where each author
could make a brief statement about work that either had been done or was needed,
with the goal of contributing to the discussion of one or more working groups.
There were~24 lightning talks submitted; after a peer-review process, 16 of
those were accepted, as discussed further in Section~\ref{sec:lightning}.
